final_project_draft

### 2022-04-04 draft.Rmd
April 4th graded before class commit.

plot1 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
  scale_colour_viridis_d()

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
  scale_colour_viridis_d()

    scale_x_discrete("Amount Donated", labels = abbreviate)

scale_x_discrete(breaks = c("0e+00", "1e+05", "2e+05", "3e+05", "4e+05"),
                  labels = c("0", "100", "200", "300", "400"))

ggplotly(plot1, tooltip = "label") 
```

## Owners Who Donate The Most Frequently and How Much 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner, League) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

@@

ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = League)) +
  geom_point() +
  labs(title = "Owners Who Have Made the Most Donations",
       y = "Owners",
       x = "Amount Donated",
       colour = "League") +
  theme_hc() +
  scale_colour_viridis_d()

plot2 <- ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = League)) +
  geom_point() +
  labs(title = "Owners Who Have Made the Most Donations",
       y = "Owners",
       x = "Amount Donated",
       colour = "League") +
  theme_hc() +
  scale_colour_viridis_d()

@@

## Going off Second Political Donations Visualization
```{r}
library(knitr)
library(pander)
library(tidyverse)

owner_rank2 <- pol_donations %>% group_by(Owner, Team) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 65)

kable(owner_rank2, caption = "Frequency of Donations from 2016 to 2020",
      col.names = c("Owner", "Team", "Amount of Donations Made"))
```

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(title = "Count of Donations",
       x = "Political Party",
       y = "Count") +
  theme_hc()
```

```{r}
owner_rank2
```

@@

ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
  geom_point() +
  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
  coord_flip() +
  labs(x = "Recipients",
       y = "Count") +
  labs(title = "Organizations Receiving Most Donations Across All Leagues") +
  theme_hc() +
  scale_colour_brewer(palette = "Dark2")
```

## Blockbusters
```{r, message = FALSE, warning = FALSE, echo = FALSE}
blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
blockbusters
```

@@

## 
```{r}
blockbusters

@@

library(ggrepel)
ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
  geom_point() +
  geom_label_repel(data = interest, aes(label = film_title)) +
  geom_point(data = interest2, aes(x = release_year, y = domestic_gross)) +
  geom_label_repel(data = interest2, aes(label = film_title))

ggplot(data = blockbusters, aes(x = release_year, y = film_budget)) +
  geom_hex() +
  labs(x = "Release Year",
       y = "Film Budget") 
```

@@

plot3 <- ggplot(data = nirvana, aes(x = order, y = Popularity, label = Popularity, colour = Popularity)) +
  geom_point() +
  geom_segment(aes(x = order, xend = order, y = 0, yend = Popularity)) +
  coord_flip() +
  labs(title = "Most Popular Nirvana Songs",
       colour = "Popularity", 
       x = " ",
       y = " ") +
  theme_hc() +
  scale_colour_viridis_b()

@@

```{r}
beatles <- history_of_rock %>% filter(artist == "The Beatles")

plot10 <- ggplot(data = beatles, aes(x = release_date, y = popularity)) +
  geom_line() +
  geom_point() +
  labs(x = "Release Date",
       y = "Popularity")

@@

beatles %>% arrange(desc(popularity)) 
```

>>>>

plot1 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "What Influence Could NFL Team Owners Have on Elections?",
       colour = "Political Party") +
  scale_colour_viridis_d() +
  theme_bw()

ggplotly(plot1, tooltip = "label")

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw()
```

## Table of Owners Who Make the Most Donations
```{r}
library(knitr)
library(pander)
library(tidyverse)
library(kableExtra)

owner_rank2 <- pol_donations %>% group_by(Owner, Team, League) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 65)

kable(owner_rank2, caption = "Who Makes the Most Donations Across All Leagues?",
      col.names = c("Owner", "Team", "League", "Amount of Donations Made")) %>%
  kable_classic()
```

## How Much Do They Donate? 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner, League) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

@@

ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Much Do They Donate?",
       y = "Owners",
       x = "Amount Donated",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom")

plot2 <- ggplot(data = frequent, aes(x = amount, y = Owner, label = Recipient, colour = Party)) +
  geom_point() +
  labs(title = "How Much Do They Donate & To Who?",
       y = "Owners",
       x = "Amount Donated",
       colour = "Party") +
  theme_grey() +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom")

@@

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(title = "Count of Donations by Political Party?",
       x = "Political Party",
       y = "Count") +
  theme(legend.position = "bottom") +
  geom_label(data = cj_party, aes(label = n), show.legend = FALSE) 
```

## What Are Some of These Organizations? 
```{r}
organizations <- charles_johnson %>% group_by(Recipient, Party) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 2)

kable(organizations, caption = "What Are Some Organizations Charles Johnson Donates To?",
      col.names = c("Recipient", "Political Party", "Amount of Donations Made"))  %>%
  kable_classic()
```

@@

ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
  geom_point() +
  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
  coord_flip() +
  labs(x = "Recipients",
       y = "Count") +
  labs(title = "Organizations Receiving Most Donations Across All Leagues") +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom")
```

## Blockbusters: A blockbuster is a Hollywood movie that's made with a large budget and big stars. A true blockbuster is extremely popular and brings in a lot of money (https://www.vocabulary.com/dictionary/blockbuster). 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
blockbusters
```

@@

## Has the Budget for Blockbusters Increased Throughout Time? 
```{r}
ggplot(data = blockbusters, aes(x = release_year, y = film_budget, colour = release_year)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm") +
  labs(x = "Release Year",
       y = "Film Budget",
       title = "Has the Budget for Blockbusters Increased Throughout Time?",
       subtitle = "Film Budget for Blockbuesters: 1977-2019") +
  theme_bw() +
  scale_colour_viridis_c() +
  theme(legend.position = "none")

ggplot(data = blockbusters, aes(x = release_year, y = film_budget)) +
  geom_hex() +
  geom_smooth(se = FALSE, method = "lm") +
  labs(x = "Release Year",
       y = "Film Budget", 
       title = "Has the Budget for Blockbusters Increased Throughout Time?",
       subtitle = "Film Budget for Blockbuesters: 1977-2019") +
  theme_bw() 
```

## Which American/Domestic Distributor Has Produced the Most Blockbusters 1977-2019
```{r}
blockbusters3 <- blockbusters %>% group_by(domestic_distributor) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  mutate(order = fct_reorder(.f = domestic_distributor, .x = n)) %>%
  filter(!n == 1)

ggplot(data = blockbusters3, aes(x = order, y = n, fill = order)) +
  geom_col() +
  coord_flip() +
  geom_label(data = blockbusters3, aes(label = n), show.legend = FALSE) +
  labs(x = "Amount of Films Produced",
       y = "Domestic Distributor",
       title = "Amount of Blockbusters Produced by Domestic Distributors: 1977-2019") +
  theme_bw() +
  theme(legend.position = "none")
```

## Work in Progress 
```{r}
blockbusters

@@

library(ggrepel)
ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
  geom_point() +
  geom_label_repel(data = interest, aes(label = film_title)) +
  geom_point(data = interest2, aes(x = release_year, y = domestic_gross)) +
  geom_label_repel(data = interest2, aes(label = film_title))
```

@@

plot3 <- ggplot(data = nirvana, aes(x = order, y = Popularity, label = Popularity, colour = Popularity)) +
  geom_point() +
  geom_segment(aes(x = order, xend = order, y = 0, yend = Popularity)) +
  coord_flip() +
  labs(title = "Most Popular Nirvana Songs: 1991-2018",
       colour = "Popularity", 
       x = " ",
       y = " ") +
  theme_bw() +
  scale_colour_viridis_b() +
  theme(legend.position = "none")

@@

## Trying to Make Density Ridges Plot 
```{r}
## install.packages("ggridges")
library(ggridges)

nirvana_small <- nirvana %>% slice(1:5) %>%
  mutate(order = fct_reorder(.f = name, .x = valence))
ggplot(data = nirvana_small, aes(x = order, y = valence)) +
  geom_density_ridges() +
  coord_flip() +
  labs(x = "Title",
       y = "Valence")
```

## Works in Progress - Simple Visualizations
```{r}
nirvana_line <- nirvana %>% rename(Title = 'name')
plot10 <- ggplot(data = nirvana_line, aes(x = Release_Date, y = Popularity, label = Title)) +
  geom_line() +
  geom_point(colour = "darkolivegreen") +
  labs(x = "Release Date",
       y = "Popularity",
       title = "Comparing Popularity by Release Date") +
  theme_bw() +
  theme(legend.position = "none")

@@

table <- history_of_rock %>% group_by(artist) %>%
  summarise(mean = mean(popularity)) %>%
  arrange(desc(mean)) %>%
  slice(1:10)

top10 <- history_of_rock %>% arrange(desc(popularity)) %>% slice(1:10)
```
